Research log

### 2023-04-25 docs/half_games.rmd
multiple regression with prior

@@

E2.half_game_first_clicks <- E2.half_game_click_log %>%
  filter(click_number==1) %>%
  group_by(i,j, grid_number,test_part) %>%
  summarise(n=n()) %>%
  ungroup() %>%
  complete(i,j,grid_number,test_part,fill=list(n=0)) %>%
  group_by(grid_number,test_part) %>%
  mutate(n=n/sum(n), x=i*5+j);

@@

>>>>

boardA <- "NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,1,1,0,0,NA,NA,0,NA,NA,1,1,NA,NA,NA"
posteriorA <- boardA%>%get_likelihood();
plot_posterior(posteriorA,'likelihoodA');

boardB <- "NA,NA,NA,NA,0,NA,NA,0,NA,NA,NA,NA,NA,NA,0,NA,NA,1,0,NA,NA,NA,1,NA,1"
posteriorB <- boardB%>%get_likelihood();
plot_posterior(posteriorB,'likelihoodB');

@@

E2.half_game_board_A <- c(12,13,14,15,18,21,22)
E2.half_game_board_B <- c(5,8,15,18,19,23,25)

E2.half_game_first_clicks <- E2.half_game_click_log %>%
  filter(click_number==1) %>%
  group_by(i,j, grid_number,test_part) %>%
  summarise(n=n()) %>%
  ungroup() %>%
  complete(i,j,grid_number,test_part,fill=list(n=0)) %>%
  group_by(grid_number,test_part) %>%
  mutate(n=n/sum(n), x=i*5+j) %>%
  mutate(n = ifelse(grid_number=='A' & (i*5+j+1) %in% E2.half_game_board_A, NaN, n),
         n = ifelse(grid_number=='B' & (i*5+j+1) %in% E2.half_game_board_B, NaN, n));

@@

```{r incorporating prior}

E2.prior_all <- E2.click_log %>%
  group_by(i,j)%>%
  summarise(n=n()) %>%
  mutate(p=n/sum(n),
         flat_position = 1+i*5+j)

E2.prior_np <- E2.click_log %>%
  filter(test_part=='nonpretend')%>%
  group_by(i,j)%>%
  summarise(n=n()) %>%
  mutate(p=n/sum(n),
         flat_position = 1+i*5+j)

E2.prior_first <- E2.click_log %>%
  filter(click_number==1)%>%
  group_by(i,j)%>%
  summarise(n=n()) %>%
  mutate(p=n/sum(n),
         flat_position = 1+i*5+j)

E2.prior_first_np <- E2.click_log %>%
  filter(click_number==1 & test_part=='nonpretend')%>%
  group_by(i,j)%>%
  summarise(n=n()) %>%
  mutate(p=n/sum(n),
         flat_position = 1+i*5+j)

E2.prior_first5 <- E2.click_log %>%
  filter(click_number<6)%>%
  group_by(i,j)%>%
  summarise(n=n()) %>%
  mutate(p=n/sum(n),
         flat_position = 1+i*5+j)

E2.prior_first5np <- E2.click_log %>%
  filter(click_number<6 & test_part=='nonpretend')%>%
  group_by(i,j)%>%
  summarise(n=n()) %>%
  mutate(p=n/sum(n),
         flat_position = 1+i*5+j)

plot_prior <- function(prior,file_name) {
  prior <- scan(text= prior, what = numeric(), sep="," , quiet = TRUE);
  board_df <- data.frame(i=rep(c(1,2,3,4,5),each=5),j=rep(c(1,2,3,4,5),5),prior=prior);
  p <- ggplot(board_df,aes(x=j,y=i,fill=prior)) +
    geom_tile() +
    coord_equal() +
    scale_x_continuous(breaks=c()) +
    scale_y_continuous(breaks=c(),trans='reverse') +
    scale_fill_gradient(low='#649bc8',high='#c83237', na.value ='white')+
    labs(x='',y='') +
    theme_classic();

  return(p)

 p<- plot_prior(paste(E2.prior_all$p,collapse=','),'priorall');
 p<- plot_prior(paste(E2.prior_np$p,collapse=','),'priornp');
 p<- plot_prior(paste(E2.prior_first$p,collapse=','),'priorfirst');
 p<- plot_prior(paste(E2.prior_first_np$p,collapse=','),'priorfirstnp');
 p<- plot_prior(paste(E2.prior_first5$p,collapse=','),'priorfirst5');
 p<- plot_prior(paste(E2.prior_first5np$p,collapse=','),'priorfirst5np');
